\documentclass[12pt]{article}

\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage{mdwlist}
\usepackage{float}
\usepackage{listings}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\usepackage{hyperref}


% christos: these look closer to NSF specs\dots
\setlength{\oddsidemargin}{0.0in}
\setlength{\evensidemargin}{0.0in}
\setlength{\textwidth}{6.5in}
\setlength{\headheight}{0.0in}
\setlength{\topmargin}{0.0in}
% \setlength{\textheight}{9.0in}
\setlength{\textheight}{9in}
\addtolength{\textheight}{-\topmargin}
\addtolength{\textheight}{-\headheight}
\addtolength{\textheight}{-\headsep}
\addtolength{\textheight}{-\footskip}



\begin{document}

\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\bit}{\begin{itemize*}}
\newcommand{\eit}{\end{itemize*}}
\newcommand{\goal}[1]{ {\noindent {$\Rightarrow$} \em {#1} } }
\newcommand{\hide}[1]{}
\newcommand{\comment}[1]{ {\footnotesize {#1} } }
\newtheorem{lemma}{Lemma}
\newtheorem{theorem}{Theorem}
\newtheorem{proof}{Proof}
\newtheorem{defn}{Definition}
\newtheorem{algo}{Algorithm}
\newtheorem{observation}{Observation}

\title{Graph Mining Using SQL}


\author{ 
	{\em Ye Zhou} \\
	    School of Computer Science \\
	    CMU\\
	    {\tt yezhou@cs.cmu.edu}
	 \and
	 {\em Jin Hu} \\
	     School of Computer Science \\
	    CMU\\
	     {\tt jinh@cs.cmu.edu}
}


\maketitle
\begin{abstract}
    \input{000abstract}
\end{abstract}

\section{Introduction}
    \label{sec:intro}
    \input{010intro}

\section{Survey}
    \label{sec:survey}
    \input{020survey}

\section{Proposed Method}
    \label{sec:proposed}
    \input{030method}


\section{Experiments}
    \label{sec:experiments}
    \input{040experiments}

\section{Conclusions}
    \label{sec:conclusions}
    \input{050conclusions}


\bibliography{project}
\bibliographystyle{plain}
\begin{thebibliography}{1}

\bibitem{kang2009}
U Kang
, \emph{PEGASUS: Mining Peta-Scale Graphs}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax ICDM, 2009.

\bibitem{kang2012}
U Kang
, \emph{GBASE: an efficient analysis platform for large graphs}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax VLDB, 2012.

\bibitem{kang2010}
U Kang
, \emph{HADI: Mining Radii of Large Graphs}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax ACM Transactions on Knowledge Discovery from Data, 2010.

\bibitem{danai2011}
Danai Koutra
, \emph{Unifying Guilt-by-Association Approaches: Theorems and Fast Algorithms}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax ECML PKDD, 2011.

\bibitem{Ignacio2005}
Danai Koutra
, \emph{k-core decomposition: a tool for the visualization of large scale networks}, 3rd~ed.\hskip 1em plus
  0.5em minus 0.4em\relax Advances in Neural Information Processing Systems, 2005.

\end{thebibliography}


\newpage
\appendix
\section{Appendix}
\input{099appendix}

\newpage
\pagenumbering{roman}
\tableofcontents


\end{document}
